Democratizing Secure Two-Party Computation

### 2017-10-22 OaklandSubmission/ld.tex
typo

The rule ({\sc{T-Cons}}) assigns the label $\mathcal{P}$ to the
constants, as the constants are always public. Rule ({\sc{T-Add}})
compiles an addition to either public addition ($+_{\mathcal{P}}$) or
secret addition using an arithmetic circuit ($+_{\mathcal{A}}$). As
our compiler is cryptographic cost aware, it never compiles the
addition to boolean addition $+_{\mathcal{B}}$. In a similar manner,
rule ({\sc{T-Gt}}) compiles $e_{1} > e_{2}$ to either public comparison
or secret comparison using boolean circuits. The rule for conditional
({\sc{T-Cond}}) has two cases: when the conditional expression $e$ is of
type $\kw{bool}^{\mathcal{P}}$, both the branches have a base type
$\sigma^{\ell'}$, for an arbitrary $\ell'$, and the conditional is
compiled to public conditional, whereas when the conditional
expression has type $\kw{bool}^{\mathcal{B}}$, $\ell'$ is also
$\mathcal{B}$, and the conditional is compiled to a secret conditional
using a boolean circuit. Note that we restrict the type of the branches
to be of base type. Rule ({\sc{T-Read}}) types an array read. It checks
that the array index $e$ is public, and uses a static bounds checking
judgment $\Gamma \models e < n$ to prove that the array index is in
bounds. Section~\ref{sec:impl} discusses our implementation of bounds
checking. Rule ({\sc{T-Inp}}) picks a label $m$ for the input. Finally,
rule ({\sc{T-Sub}}) is the subsumtion rule that coerces an expression of
type $\sigma^{\ell}$ to an expression of type $\sigma^{m}$ using the
coerce expression. Importantly, secrets cannot be coerced to public
values.

>>>>

The rule ({\sc{T-Cons}}) assigns the label $\mathcal{P}$ to the
constants, as the constants are always public. Rule ({\sc{T-Add}})
compiles an addition to either public addition ($+_{\mathcal{P}}$) or
secret addition using an arithmetic circuit ($+_{\mathcal{A}}$). As
our compiler is cryptographic cost aware, it never compiles the
addition to boolean addition $+_{\mathcal{B}}$. In a similar manner,
rule ({\sc{T-Gt}}) compiles $e_{1} > e_{2}$ to either public comparison
or secret comparison using boolean circuits. The rule for conditional
({\sc{T-Cond}}) has two cases: when the conditional expression $e$ is of
type $\kw{bool}^{\mathcal{P}}$, both the branches have a base type
$\sigma^{\ell'}$, for an arbitrary $\ell'$, and the conditional is
compiled to public conditional, whereas when the conditional
expression has type $\kw{bool}^{\mathcal{B}}$, $\ell'$ is also
$\mathcal{B}$, and the conditional is compiled to a secret conditional
using a boolean circuit. Note that we restrict the type of the branches
to be of base type. Rule ({\sc{T-Read}}) types an array read. It checks
that the array index $e$ is public, and uses a static bounds checking
judgment $\Gamma \models e < n$ to prove that the array index is in
bounds. Section~\ref{sec:impl} discusses our implementation of bounds
checking. Rule ({\sc{T-Inp}}) picks a label $m$ for the input. Finally,
rule ({\sc{T-Sub}}) is the subsumption rule that coerces an expression of
type $\sigma^{\ell}$ to an expression of type $\sigma^{m}$ using the
coerce expression. Importantly, secrets cannot be coerced to public
values.
